---
title: "Assignment 05 R"
author: "R. Schütz"
date: "`r Sys.Date()`"
output: html_document
---

# General

Github-Projekt URL: https://github.com/Borschu/Assignment_05

Install / load packages:
```{r}

#install.packages("httr")
library("httr")

library("tidyverse")

#install.packages("magrittr")
library("magrittr")

library("maps")
```

# Getting to know the API

Limit: 5000 API calls per day
rate limit: 5 requests per second
Only the 1000th item can be retrieved (size*page <1000)

```{r}
# read file for api key
source("C:/Users/schur/OneDrive/Dokumente/Studium/Data Science Master Tübingen/1. Semester/Data Science Project Management/Assignment/key_assignment_5.R")
```

# Interacting with the API - the basics

## (7)
```{r}
# search for all venues in Germany (where countryCode = DE)
res_venue_ger <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues/",
                     query = list(apikey = ticketmaster_key,
                                  "countryCode" = "DE"))

# get content of the query and print it
con_venue_ger <- content(res_venue_ger)
con_venue_ger
```
We can see different lists that are nested in each other. For each venue multiple attributes (name, type, id, test, url,...) exist. For some of the attributes a specific value is directly given (for example for name -> Gruenspan (first venue)). Some of these attributes have another layer (for example location has a further layer for longitude / latitude). At the end of the printed output you an see some statistics about the request. For example that in total 238 pages or 4745 Elements (venues in Germany) exist.

## (8)

```{r}
## name
# get the names of the venue
name <- map_chr(con_venue_ger$`_embedded`$venues, "name")

## city
# create empty city-vector
city <- c()
# loop over all 20 venues
for (i in 1:20){
  # add name to city vector
  city <- append(city, con_venue_ger$`_embedded`$venues[[i]]$city$name)
}


## postal code 
# create postal code vector (map_dbl doesnt work), default to NA -> if there is no Postal code then NA
postalCode <- as.double(map_chr(con_venue_ger$`_embedded`$venues, "postalCode", .default = NA))


## address
# create empty address vector
address <- c()
# append values via loop
# if there is no such value create NA
for (i in 1:20){
  address <- append(address, ifelse(is.null(con_venue_ger$`_embedded`$venues[[i]]$address$line1),
                                    NA, con_venue_ger$`_embedded`$venues[[i]]$address$line1))
}

## url 
# create url vector
url <- map_chr(con_venue_ger$`_embedded`$venues, "url")

## longitude 
# create empty longitude-vector
longitude <- c()
# loop over all 20 venues
# if the value doesn exist ->NA, else append by the specific value
for (i in 1:20){
  # add value to longitude vector
  longitude <- append(longitude, ifelse(is.null(con_venue_ger$`_embedded`$venues[[i]]$location$longitude),
                                    NA, con_venue_ger$`_embedded`$venues[[i]]$location$longitude))
}
# change datatype to double
longitude <- as.double(longitude)

## latitude
# create empty latitude-vector
latitude <- c()
# loop over all 20 venues
# if the value doesn exist ->NA, else append by the specific value
for (i in 1:20){
  # add value to longitude vector
  latitude <- append(latitude, ifelse(is.null(con_venue_ger$`_embedded`$venues[[i]]$location$latitude),
                                    NA, con_venue_ger$`_embedded`$venues[[i]]$location$latitude))
}
# change datatype to double
latitude <- as.double(latitude)

# create dataframe with vectors
venue_ger <- data.frame(name, city, postalCode,address, url, longitude, latitude)


```

# Interacting with the API - advanced

```{r}
# create function to get all venues for a specific country
create_df <- function(countryCode){
  # get the first page
  page <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues/",
                     query = list(apikey = ticketmaster_key,
                                  "countryCode" = countryCode))
  # let the system sleep because of the rate limit
  Sys.sleep(0.2)
  # get content of page
  con_page <- content(page)
  # get nr. of pages and nr. of entries per page
  nr_pages <- con_page$page$totalPages
  nr_entries <- con_page$page$size
  
  # create empty dataframe (after the first iteration this dataframe is used for the first )
  df_all <- data.frame(name = character(), 
                       city = character(), 
                       postalCode = double(),
                       address = character(), 
                       url = character(), 
                       longitude = double(), 
                       latitude = double())
  
  # loop over all pages
  for (p in 0:(nr_pages-1)){
    
    # often the API request throws an error when looping over multiple pages
    # thats why the while loop is introduced
    control <- NULL
    # while loop checks if control variable is null
    while(is.null(control)){
      # get venues for a specific contry code and specific page
      page <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues/",
                     query = list(apikey = ticketmaster_key,
                                  "countryCode" = countryCode,
                                  "page" = p))
      # get content of a page
      content = content(page)
      # create controll variable
      control <- content$`_embedded`$venues
    }
    
    # the last page is usually not full
    # to get the number of elements on the last page this if-statement
    # is created
    if (p == nr_pages-1){
    nr_entries = con_page$page$totalElements %% nr_entries
    }
    
    ## name
    # get names of venues (and create a vector)
    # the .default = NA sets missings to NA
name <- map_chr(content$`_embedded`$venues, "name", .default = NA)

## city
# create empty city-vector
city <- c()
# loop over all 20 venues
for (i in 1:nr_entries){
  # add name to city vector
  city <- append(city, ifelse(is.null(content$`_embedded`$venues[[i]]$city$name),NA,
                              content$`_embedded`$venues[[i]]$city$name))
}


## postal code 
# create postal code vector (map_dbl doesnt work), default to prevent error if value is missing
postalCode <- as.double(map_chr(content$`_embedded`$venues, "postalCode", .default = NA))


## address
# create empty adress vector
address <- c()
# append values via loop
# if there is no such value create NA
for (i in 1:nr_entries){
  address <- append(address, ifelse(is.null(content$`_embedded`$venues[[i]]$address$line1),
                                    NA, content$`_embedded`$venues[[i]]$address$line1))
}

## url 
# create url vector
url <- map_chr(content$`_embedded`$venues, "url", .default = NA)

## longitude 
# create empty longitude-vector
longitude <- c()
# loop over all 20 venues
# if the value doesn exist ->NA, else append by the specific value
for (i in 1:nr_entries){
  # add name to longitude vector
  longitude <- append(longitude, ifelse(is.null(content$`_embedded`$venues[[i]]$location$longitude),
                                    NA, content$`_embedded`$venues[[i]]$location$longitude))
}
# change datatype to double
longitude <- as.double(longitude)

## latitude
# create empty latitude-vector
latitude <- c()
# loop over all 20 venues
# if the value doesn exist ->NA, else append by the specific value
for (i in 1:nr_entries){
  # add name to longitude vector
  latitude <- append(latitude, ifelse(is.null(content$`_embedded`$venues[[i]]$location$latitude),
                                    NA, content$`_embedded`$venues[[i]]$location$latitude))
}
# change datatype to double
latitude <- as.double(latitude)

# print p to track the progress of the function
print(p)

# create dataframe
df_page <- data.frame(name, city, postalCode,address, url, longitude, latitude)

# bind the dataframes together
df_all <- rbind(df_all, df_page)

# let system sleep because of the rate limit
Sys.sleep(0.2)

  }
  
  # return dataframe
  return(df_all)
}

# create dataframe with venues for Germany
venue_de <- create_df("DE")

# print head of dataframe
print("The first 10 rows of the dataframe: ")
print(head(venue_de,10))

# print dimension of the dataframe
print("Dimensions of the dataframe: ")
print(dim(venue_de))

```

# Visualizing the extracted data

## (10)
```{r}
# based on the code that is mentioned in the assignment the venues are visualized
ggplot(venue_de) +
borders("world", "Germany", colour = "black", fill = "grey90") +
  # add geom_point to create points for the locations
  # add alpha to make points transparent (-> to make overlaying points visible)
  geom_point(aes(longitude,latitude),
             alpha = 0.4)+
theme_void() +
coord_quickmap() +
labs(title = "Event locations across Germany",
caption = "Source: ticketmaster.com") +
theme(title = element_text(size=8, face='bold'),
plot.caption = element_text(face = "italic"))
```

## (11)
```{r}
# create NAs for latitude / longitude if  outside from germany
# write a function to make life easier for the next tasks

adapt_long_lat <- function(df_country,long_lower,long_upper,lat_lower,lat_upper){
  # change the values to NA for long / lat if the values are outside the long/lat
  # range 
  df_country$longitude[df_country$longitude < long_lower] <- NA
  df_country$longitude[df_country$longitude > long_upper] <- NA
  df_country$latitude[df_country$latitude < lat_lower] <- NA
  df_country$latitude[df_country$latitude > lat_upper] <- NA
  
    return(df_country)
}

#longitude is outside the range (5.866, 15.042) or
#where the value of latitude is outside the range (47.270, 55.059)
venue_de_adjust <- adapt_long_lat(venue_de,5.866, 15.042,47.270, 55.059)

# visualize venues with adapted longitude /latitude
ggplot(venue_de_adjust) +
borders("world", "Germany", colour = "black", fill = "grey90") +
  # add geom_point to create points for the locations
  # add alpha to make points transparent (-> to make overlaying points visible)
  geom_point(aes(longitude,latitude),
             alpha = 0.4)+
theme_void() +
coord_quickmap() +
labs(title = "Event locations across Germany",
caption = "Source: ticketmaster.com") +
theme(title = element_text(size=8, face='bold'),
plot.caption = element_text(face = "italic"))
```


# Event locations in other countries

## (12)
In this task the venues for Italy will be examined.

```{r}
# Create dataframe with venues in italy
venue_it <- create_df("IT")

# visualize the venues
ggplot(venue_it) +
borders("world", "Italy", colour = "black", fill = "grey90") +
  # add geom_point to create points for the locations
  # add alpha to make points transparent (-> to make overlaying points visible)
  geom_point(aes(longitude,latitude),
             alpha = 0.4)+
theme_void() +
coord_quickmap() +
labs(title = "Event locations across Italy",
caption = "Source: ticketmaster.com") +
theme(title = element_text(size=8, face='bold'),
plot.caption = element_text(face = "italic"))

# adjust the longitude / latitude column based on the latitude / longitude range
# NAs if outside the latitude / longitude range
venue_it_adjust <- adapt_long_lat(venue_it,6.616667, 18.516667, 37.933333, 47.083333)


# visualize venues with adjusted longitude / latitude
ggplot(venue_it_adjust) +
borders("world", "Italy", colour = "black", fill = "grey90") +
  # add geom_point to create points for the locations
  # add alpha to make points transparent (-> to make overlaying points visible)
  geom_point(aes(longitude,latitude),
             alpha = 0.4)+
theme_void() +
coord_quickmap() +
labs(title = "Event locations across Italy",
caption = "Source: ticketmaster.com") +
theme(title = element_text(size=8, face='bold'),
plot.caption = element_text(face = "italic"))

```

